full title

### 2020-11-17 paper/pldi21/implementation.tex
Added some more descriptions on Proxy objects.

\paragraph{Sealed Symbolic Values.}
The main challenge of implementing dynamic shortcut is to support the sealed
symbolic execution on the existing JavaScript engine.  We leverage the \jscode{Proxy}
object introduced in ECMAScript 6 (2015, ES6)~\cite{es6}, which allows
developers to handle the internal behaviors of specific objects (such as
property reads and writes, implicit conversions, etc.).  When the dynamic
analyzer constructs the execution environments at the start of the dynamic
shortcut, it creates revoked \jscode{Proxy} objects to represent abstract values
via the following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  const r = Proxy.revocable(function() {}, {});
  r.revoke();
  return r.proxy;
}
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol as a revocable proxy object with a dummy
function object without any handlers and revokes it by
\jscode{revocable.revoke()} to not allow any access of the symbol.  Thus, the
variable \jscode{y} successfully points to the same symbol stored in \jscode{x}
but the program throws a \jscode{TypeError} in line 8 because \jscode{x + 1}
requires the actual value of the symbol.  Using this idea, we successfully
extend the JavaScript engine to support a sealed symbolic execution.

>>>>

\paragraph{Sealed Symbolic Values.}
The main challenge of implementing dynamic shortcut is to support the sealed
symbolic execution on the existing JavaScript engine.  To represent an abstract
value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
(2015, ES6)~\cite{es6}, which allows developers to handle the internal behaviors
of specific objects (such as property reads and writes, implicit conversions,
etc.).  We are inspired by \textsc{Mimic}~\cite{mimic} using \jscode{Proxy} to
capture accesses from the inside of opaque functions.  When the dynamic analyzer
constructs the execution environments at the start of the dynamic shortcut, it
creates revoked \jscode{Proxy} objects to represent each abstract values via the
following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  const r = Proxy.revocable(function() {}, {});
  r.revoke();
  return r.proxy;
}
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol as a revocable proxy object with a dummy
function object without any handlers and revokes it by
\jscode{revocable.revoke()} to not allow any access of the symbol.  The revoked
object throws a \jscode{TypeError} when the object faces 13 kinds of operations
so we can determine whether or not the seal is open.  For example, the variable
\jscode{y} successfully points to the same symbol stored in \jscode{x} but the
program throws the \jscode{TypeError} in line 8 because \jscode{x + 1} requires
the actual value of the symbol.  Moreover, we instrument unary and binary
operations on Jalangi to fully cover accesses on the symbol beyond 13 traps
provided by \jscode{Proxy}.  Using this idea, we successfully extend the
JavaScript engine to support a sealed symbolic execution.
